Cumulative Score Plots Experiment 2

### 2019-12-04 Experiment_2/exp2_score_plots.Rmd
plot bug fix

```{r}
ggplot(data = exp2_cum_score, aes(x = t, y=acc_sum, group = part_num)) + 
  geom_line(aes(color= Best_model))
```

>>>>

```{r}
ggplot(data = exp2_cum_score, aes(x = t, y=acc_sum, group = part_num)) + 
  geom_line(aes(color= Best_model)) +
  scale_x_continuous(minor_breaks = seq(0 , 180, 10), breaks = seq(0, 180, 60))
```
